Invited talks marked with *.
\vspace{0.2cm}

\textcolor{color1}{\textbf{Talks at conferences:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{7.} &  & \textbf{Transformers plus Normalizing Flows for parameter estimation of overlapping gravitational waves in next-generation detectors.}
\newline{}
\textit{\href{https://agenda.infn.it/event/43565/overview/}{EuCAIFCon 2025} - Cagliari, Italy}, 16-20 June 2025.
\vspace{0.05cm}\\
%
\textbf{6.} &  & \textbf{Inferring Population Properties of Galactic Binaries in LISA with Simulation Based Inference.}
\newline{}
\textit{\href{https://uofgravity.github.io/aislands/}{AIslands 2025} - Rothesay, Isle of Bute (Scotland)}, 13-15 May 2025.
\vspace{0.05cm}\\
%
\textbf{5.} & * & \textbf{Machine Learning and Simulation Based Inference for ET \& LISA.}
\newline{}
\textit{\href{https://davidegerosa.com/thuram/}{THURAM 2025} - GSSI, L'Aquila (Italy)}, 7-9 May 2025.
\vspace{0.05cm}\\
%
\textbf{4.} &  & \textbf{Deep learning to detect gravitational waves from binary close encounters: Fast parameter estimation with normalizing flows.}
\newline{}
\textit{LIGO-Virgo-KAGRA (LVK) Collaboration Meeting (Baton Rouge, USA)}, 11-14 Mar. 2024.
\newline{}
\textcolor{color1}{$\bullet$} (online).
\vspace{0.05cm}\\
%
\textbf{3.} &  & \textbf{Deep learning to detect gravitational waves from binary close encounters: Fast parameter estimation with normalizing flows.}
\newline{}
\textit{\href{https://indico.ego-gw.it/event/666/overview}{Integrated Activities for the High Energy Astrophysics Domain (AHEAD2020) Workshop} - European Gravitational Wave Observatory (EGO), Cascina}, 4-5 Mar. 2024.
\vspace{0.05cm}\\
%
\textbf{2.} &  & \textbf{GW from Binary Close Encounters: Analysis with Normalizing Flow.}
\newline{}
\textit{Virgo Week - European Gravitational Wave Observatory (EGO), Cascina}, 5-9 Feb. 2024.
\vspace{0.05cm}\\
%
\textbf{1.} &  & \textbf{GW from Binary Close Encounters: Analysis with Normalizing Flow.}
\newline{}
\textit{Burst (LVK) Collaboration Meeting}, 20 Dec. 2023.
\newline{}
\textcolor{color1}{$\bullet$} online.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Talks at department seminars:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{1.} & * & \textbf{Probabilistic Machine Learning for the study of burst sources.}
\newline{}
\textit{Virgo Pisa Internal Workshop (INFN Pisa)}, 22-23 May 2024.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Posters at conferences:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{3.} &  & \textbf{HYPERION: a Normalizing Flow based pipeline for the rapid parameter estimation of eccentric Close Encounters.}
\newline{}
\textit{\href{https://agenda.infn.it/event/40101/overview}{GraSP24 - Gravity Shape Pisa 2024 Conference}}, 23-25 Oct. 2024.
\vspace{0.05cm}\\
%
\textbf{2.} &  & \textbf{HYPERION: a Normalizing Flow based pipeline for the rapid parameter estimation of eccentric Close Encounters.}
\newline{}
\textit{\href{https://agenda.infn.it/event/38056/overview}{V GraviGammaNu Workshop 2024} (Bari)}, 9-11 Oct. 2024.
\vspace{0.05cm}\\
%
\textbf{1.} &  & \textbf{Gravitational Waves from Binary Close Encounters: Fast Parameter Estimation with Normalizing Flows.}
\newline{}
\textit{LIGO-Virgo-KAGRA (LVK) Collaboration Meeting (Toyama, Japan)}, 11-14 Sep. 2023.
\vspace{0.05cm}\\
%
\end{longtable} }